\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-04-14 forwards-and-backwards.tex
Update on Overleaf.

\begin{figure}
    \begin{center}
        \includegraphics{figures/conceptual_figure}
    \end{center}
    \caption{
        Conceptual figure of the model.
        \textbf{(A)} Example plot of $\gamma$, $\mu$, and $F$
        (calculated with $r=1$) against scaled local population density.
        In this example, both birth and death rates increase with population density,
        but death increases faster,
        and equilibrium occurs where they cross
        (and hence where $F=0$).
        \textb{(B)} Cartoon of interaction ($\epsilon$) and dispersal ($\sigma$) distances.
        \label{fig:model_setup}
    }
\end{figure}

@@

\begin{definition}[Martingale Problem Characterisation]
    \label{Def: Rescaled Models}
We define $(\eta^{\theta}_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
with initial condition $\eta^{\theta}_0$,
such that for all smooth functions $f \in C^{2}_{0}(\mathbb{R}^d)$,
\begin{equation}
    \label{eq: Pre-limit Martingale Characterisation}
\begin{aligned}
M^{\theta}_t(f)
&:=  \langle f,\eta^{\theta}_t \rangle
        -\langle f,\eta^{\theta}_0 \rangle
 \\ &\qquad {}
 -  \int_{0}^{t}\bigg\{
        \int\left(   \int \theta
     \left(
        f(z)r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
            -f(x)r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
        \\ & \qquad \qquad \qquad \qquad {} \times
                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)
     \\ & \qquad {} +\int 
     f(x)F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
     \eta^{\theta}_{s}(dx)
    \bigg\} ds
\end{aligned}    
\end{equation}
is a martingale with quadratic variation
\begin{equation}
\begin{aligned} \relax
[ M^{\theta}_t(f)] =& 
\frac{\theta}{N} \int_{0}^{t}\bigg\{
\langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
\int f^2(y)r\big(y,\rho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
,\eta^{\theta}_{s}(dx)\rangle\\
& \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds. 
\end{aligned}    
\end{equation}

@@

%%%%%%%%%%
\paragraph{Fisher--KPP:}
A great deal more attention has been paid to the classical Fisher-KPP equation,
\begin{align} \label{eqn:fkpp}
    v_t = v_{xx} + v (1-v) .
\end{align}
In this case,
even though we do not have an explicit formula for the wave shape,
these methods give us information about ancestral lineages.
The equation has non-negative travelling wave solutions of speed $c$ for all $c \geq 2$, 
but started from any compact perturbation of a Heaviside function, the 
solution will converge to the profile $w^F$ with the minimal wavespeed, $c=2$,
\cite{kolmogorov/petrovsky/piscounov:1937,\meanqramson:1983}.
No matter what the initial condition,
for any $t>0$ the support of the 
solution will be the whole real line. 
Since in ths case, $r = \gamma = 1$,
the generator of the motion of an ancestral lineage is
$$
    \Lgen \phi
    =
    \phi_{xx} + 2 \frac{w_x}{w} \phi_x + 2 \phi_x .
$$
Near the tip of the wave (for $x$ large), $w^F(x) \sim e^{-x}$,
so the motion of the lineage is close to Brownian motion.
On the other hand, for $x < 0$ the lineage behaves approximately as
Brownian motion with drift at rate two to the right.
This implies that
ancestral lineages are pushed into the tip of the wave,
and there is no stationary distribution.
These results agree with those of \comment{XXX}.

@@

Since 
\begin{equation}
\begin{aligned}
G'(s)=& - \frac{|A|}{2|I+As|^{3/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
      & + \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
      & \qquad \times \left\{ v^{T}B(I+Cs)^{-1}v
                            - sv^{T}BC(I+Cs)^{-2}v
                    \right\}\\
      &=\left(- \frac{|A|}{2|I+As|}+v^{T}B(I+Cs)^{-2}v
        \right)\\
      & \qquad \times
        \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),
\end{aligned}
\end{equation}
using non-negativity of $A,B,C$ we have
\begin{equation}
\label{eq: bounds on G'}
|G'(s)| \leq (|A|+||B||_{2}||v||_2^2)G(s).    
\end{equation}
As a result, we have that 
\begin{equation}
\label{eq: bounds on G}
G(s) \leq K e^{|A|+||B||_{2}||v||_2^2)s}.    
\end{equation}

Finally note that, 
$$F'(s) \leq G_1'(s)+2G_2'(s),$$
where 
$$A_1= 2\epsilon_r^{-2} \covq, ~ v_1=\epsilon_r^{-2}(w-x-\meanq), ~B_1 = 2\covq, ~C_1=2\epsilon_r^{-2} \covq,$$
and 
$$A_2= 2\epsilon_r^{-2} \covq, ~ v_2=\epsilon_r^{-2}(w-x-\meanq), ~B_2 = \covq/2, ~C_2=2\epsilon_r^{-2} \covq,$$
Substituting these quantities on Equation \eqref{eq: bounds on G'} and Equation \eqref{eq: bounds on G} shows that Equation \eqref{eqn:goal3} is satisfied as long as $\epsilon_r < \epsilon_\gamma$.
\end{proof}

\begin{lemma}[Compact Containment for the population process]
Assume that $\eta^{\theta}_0 \to \eta_0$ weakly,
then for all $T>0$, there exists some constant $C(T)$,
such that
    \begin{align}
        \IE\left[
            \sup_{0 \le t \le T}
            \langle 1, \eta^\theta_t \rangle
        \right]
        \le C(T) ,
    \end{align}
    uniformly in $\theta$.
\end{lemma}
\begin{proof}
We first take $f \equiv 1$ in Equation \eqref{eq: Pre-limit Martingale Characterisation}. We have that 
\begin{equation}
    \label{eq: Total Mass Martingale Characterisation}
\begin{aligned}
     M^{\theta}_t(1):=&  \langle 1,\eta^{\theta}_t \rangle
        -\langle 1,\eta^{\theta}_0 \rangle\\
 &-  \int_{0}^{t}\bigg\{   \int\left(   \int \theta
 \left(
        r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
            -r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)\\
& \qquad +\int F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
\eta^{\theta}_{s}(dx)\bigg\} ds
\end{aligned}    
\end{equation}
is a martingale.
Therefore, taking expectations, we have
\begin{equation}\label{eq: Total mass control generalised}
\begin{aligned}
&\mathbb{E}[\langle 1 ,\eta^{\theta}_{t}\rangle] \\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] \\
&+ \int_{0}^{t}\mathbb{E}\bigg\langle
        \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
            \left| \theta \int_{\mathbb{R}^n}
                    \big\{r\big(\rho_{r}*\eta^{\theta}_s(y)\big)-r\big(\rho_{r}*\eta^{\theta}_s(x)\big)\big\}
                    \rho_{1/\theta}(x-y)dy\right| + C_F 
                            ,\eta^{\theta}_s(dx)  \bigg\rangle ds\\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \langle 1  ,\eta^{\theta}_s(dx) \rangle ds,
\end{aligned}
\end{equation}
where the last inequality holds by Lemma \ref{lem: gamma - r radius comparison}.

@@

\subsubsection{Controlling Jumps}
To apply Aldous-Rebolledo criterion,
(or see Theorem 3.9.1 or Theorem 3.8.6 in \cite{EK})
it suffices to show that for all $f \in \mathcal{C}^2_{c}(\mathbb{R}^d)$
and $\tau \in [0,T]$, we have 
\begin{equation}
\begin{aligned}
\limsup_{s \to 0}\limsup_{\theta \to \infty}\mathbb{E}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle - \langle f, \eta^{\theta}_{\tau}\rangle \right|\right]& \to 0;\\
\limsup_{s \to 0}\limsup_{\theta \to \infty}\mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] - [M^{\theta}_{\tau}(f)] \big|\right]& \to 0.
\end{aligned}    
\end{equation}
Note that
\begin{equation}
\begin{aligned}
 & \mathbb{E}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle - \langle f, \eta^{\theta}_{\tau}\rangle \right|\right] \\
\leq & \mathbb{E}\Bigg[\bigg| \int_{\tau}^{\tau+s}\bigg\langle \theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x)) \int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{\theta}_{s}(y))-f(x)r(\rho_{r}*\eta^{\theta}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
& \qquad + F(\rho_{F}*\eta^{\theta}_{s}(x)) f(x),\eta^{\theta}_{s}(dx)  \bigg\rangle ds \bigg|\Bigg].
\end{aligned}
\end{equation}
In particular,
\begin{multline}
 \theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{\theta}_{s}(y))-f(x)r(\rho_{r}*\eta^{\theta}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
 =  f(x)\theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{r(\rho_{r}*\eta^{\theta}_{s}(y))-r(\rho_{r}*\eta^{\theta}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy\\
 + \theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{(f(y)-f(x))r(\rho_{r}*\eta^{\theta}_{s}(y))\big\}\rho_{1/\theta}(x-y)dy\\
 \leq C_{\gamma,r}||f||_{\infty} + C_{\gamma}||\Delta f||_{\infty},
\end{multline}
since the first term is bounded above by $C_{\gamma,r}f(x)$ by Lemma \ref{lem: gamma - r radius comparison}
and the second term by $C_{\gamma} \Delta f(x)$ as $r \leq 1$.

Finally,  $F(\rho_{F}*\eta^{\theta}_{s}(x)) f(x)$ is bounded above by $C_F||f||_{\infty}$, so 
\begin{multline}
\mathbb{E}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle - \langle f, \eta^{\theta}_{\tau}\rangle \right|\right] \\
\leq (C_{\gamma,r}||f||_{\infty} + C_{\gamma,r}||\Delta f||_{\infty}+C_F||f||_{\infty}) \mathbb{E}\bigg\{\int_{\tau}^{\tau+s}\bigg\langle 1,\eta^{\theta}_{s}(dx)  \bigg\rangle  ds\bigg\} \\
\leq (C_{\gamma,r}||f||_{\infty} + C_{\gamma,r}||\Delta f||_{\infty}+C_F||f||_{\infty}) \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)T}(e^s-1)\to 0
\end{multline}
as $s \to \infty$. 
This gives us bound on the first moment.

Similarly, the control on the second moment is given by Equation \eqref{eq: Control quadratic variation}.
\begin{equation}
    \label{eq: Controlling Quadratic Jumps}
\begin{aligned}
& \mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] - [M^{\theta}_{\tau}(f)] \big|\right]\\
\leq &\frac{\theta}{N} \mathbb{E} \Bigg\{ \int_{\tau}^{\tau+s}\bigg|
\langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
\int f^2(y)r\big(y,\rho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
,\eta^{\theta}_{s}(dx)\rangle\\
& \qquad \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
,\eta^{\theta}_{s}(dx)\rangle \bigg|ds \Bigg\}\\
\leq & \frac{2\theta}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma(\rho_{\gamma}*\eta^{\theta}_{s}(x))r(\rho_{r}*\eta^{\theta}_{s}(x)), \eta^{\theta}_{s}(dx) \right\rangle ds\Bigg\} \\
& + \frac{1}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma (\rho_{\gamma}*\eta^{\theta}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\rho_{r}*\eta^{\theta}_{s}(y))-r(\rho_{r}*\eta^{\theta}_{s}(x))\right) q_\theta(x,dy), \eta^{\theta}_{s}(dx) \right\rangle ds\Bigg\}\\
\leq & \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)T}(e^s-1)}{N} \to 0
\end{aligned}
\end{equation}
as $s \to 0$.

@@

    \begin{lemma}[Convergence of generators for the population process]
        As $\theta \to \infty$,
        \comment{(the generator for the prelimit)}
        converges to
        \comment{(the generator for the limit)}.
    \end{lemma}

>>>>

\begin{figure}
    \begin{center}
        \includegraphics{figures/conceptual_figure}
    \end{center}
    \caption{
        Conceptual figure of the model.
        \textbf{(A)} Example plot of $\gamma$, $\mu$, and $F$
        (calculated with $r=1$) against scaled local population density.
        In this example, both birth and death rates increase with population density,
        but death increases faster,
        and equilibrium occurs where they cross
        (and hence where $F=0$).
        \textbf{(B)} Cartoon of interaction ($\epsilon$) and dispersal ($\sigma$) distances.
        \label{fig:model_setup}
    }
\end{figure}

@@

\begin{definition}[Martingale Problem Characterisation]
    \label{Def: Rescaled Models}
We define $(\eta^{\theta}_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
with initial condition $\eta^{\theta}_0$,
such that for all smooth functions $f \in C^{2}_{0}(\mathbb{R}^d)$,
\begin{equation}
    \label{eq: Pre-limit Martingale Characterisation}
\begin{aligned}
M^{\theta}_t(f)
&:=  \langle f,\eta^{\theta}_t \rangle
        -\langle f,\eta^{\theta}_0 \rangle
 \\ &\qquad {}
 -  \int_{0}^{t}\bigg\{
        \int\left(   \int \theta
     \left(
        f(z)r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
            -f(x)r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
        \\ & \qquad \qquad \qquad \qquad {} \times
                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)
     \\ & \qquad \qquad {} +\int 
     f(x)F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
     \eta^{\theta}_{s}(dx)
    \bigg\} ds
\end{aligned}    
\end{equation}
is a martingale with quadratic variation
\begin{equation}
\begin{aligned} \relax
[ M^{\theta}_t(f)] =& 
\frac{\theta}{N} \int_{0}^{t}\bigg\{
\langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
\int f^2(y)r\big(y,\rho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
,\eta^{\theta}_{s}(dx)\rangle\\
& \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds. 
\end{aligned}    
\end{equation}

@@

%%%%%%%%%%
\paragraph{Fisher--KPP:}
A great deal more attention has been paid to the classical Fisher-KPP equation,
\begin{align} \label{eqn:fkpp}
    v_t = v_{xx} + v (1-v) .
\end{align}
In this case,
even though we do not have an explicit formula for the wave shape,
these methods give us information about ancestral lineages.
The equation has non-negative travelling wave solutions of speed $c$ for all $c \geq 2$, 
but started from any compact perturbation of a Heaviside function, the 
solution will converge to the profile $w^F$ with the minimal wavespeed, $c=2$,
\cite{kolmogorov/petrovsky/piscounov:1937,ramson:1983}.
No matter what the initial condition,
for any $t>0$ the support of the 
solution will be the whole real line. 
Since in ths case, $r = \gamma = 1$,
the generator of the motion of an ancestral lineage is
$$
    \Lgen \phi
    =
    \phi_{xx} + 2 \frac{w_x}{w} \phi_x + 2 \phi_x .
$$
Near the tip of the wave (for $x$ large), $w^F(x) \sim e^{-x}$,
so the motion of the lineage is close to Brownian motion.
On the other hand, for $x < 0$ the lineage behaves approximately as
Brownian motion with drift at rate two to the right.
This implies that
ancestral lineages are pushed into the tip of the wave,
and there is no stationary distribution.
These results agree with those of \comment{XXX}.

@@

Since 
\begin{equation}
\begin{aligned}
G'(s)=& - \frac{|A|}{2|I+As|^{3/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
      & + \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v)\\
      & \qquad \times \left\{ v^{T}B(I+Cs)^{-1}v
                            - sv^{T}BC(I+Cs)^{-2}v
                    \right\}\\
      &=\left(- \frac{|A|}{2|I+As|}+v^{T}B(I+Cs)^{-2}v
        \right)\\
      & \qquad \times
        \frac{1}{|I+As|^{1/2}}\exp(v^{T}Bs(I+Cs)^{-1}v),
\end{aligned}
\end{equation}
using non-negativity of $A,B,C$ we have
\begin{equation}
\label{eq: bounds on G'}
|G'(s)| \leq (|A|+||B||_{2}||v||_2^2)G(s).    
\end{equation}
As a result, we have that 
\begin{equation}
\label{eq: bounds on G}
G(s) \leq K e^{|A|+||B||_{2}||v||_2^2)s}, ~~   G'(s)(|A|+||B||_{2}||v||_2^2)K e^{|A|+||B||_{2}||v||_2^2)s}.  
\end{equation}

Finally note that, 
$$F'(s) \leq G_1'(s)+2G_2'(s),$$
where 
$$A_1= 2\epsilon_r^{-2} \covq, ~ v_1=\epsilon_r^{-2}(w-x-\meanq), ~B_1 = 2\covq, ~C_1=2\epsilon_r^{-2} \covq,$$
and 
$$A_2= 2\epsilon_r^{-2} \covq, ~ v_2=\epsilon_r^{-2}(w-x-\meanq), ~B_2 = \covq/2, ~C_2=2\epsilon_r^{-2} \covq,$$
Substituting these quantities on Equation \eqref{eq: bounds on G} shows that Equation \eqref{eqn:goal3} is satisfied as long as $\epsilon_r < \epsilon_\gamma$.
\end{proof}

\begin{lemma}[Compact Containment for the population process]
    \label{lem: Compact Containment}
Assume that $\eta^{\theta}_0 \to \eta_0$ weakly,
then for all $T>0$, there exists some constant $C(T)$,
such that
    \begin{align}
        \IE\left[
            \sup_{0 \le t \le T}
            \langle 1, \eta^\theta_t \rangle
        \right]
        \le C(T) ,
    \end{align}
uniformly in $\theta$.
In particular, for any $\epsilon > 0$, there exists some $K_{\epsilon}>0$ such that
\begin{equation}
\limsup_{\theta \to \infty}
    \mathbb{P}\left[\sup_{s \in [0,T]}
        \langle 1 ,\eta^{\theta}_{s}\rangle
        > K_\epsilon \right]
        \leq \frac{C(T)}{K_{\epsilon}} < \epsilon.    
\end{equation}
\end{lemma}
\begin{proof}
We first take $f \equiv 1$ in Equation \eqref{eq: Pre-limit Martingale Characterisation}. We have that 
\begin{equation}
    \label{eq: Total Mass Martingale Characterisation}
\begin{aligned}
     M^{\theta}_t(1):=&  \langle 1,\eta^{\theta}_t \rangle
        -\langle 1,\eta^{\theta}_0 \rangle\\
 &-  \int_{0}^{t}\bigg\{   \int\left(   \int \theta
 \left(
        r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
            -r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)\\
& \qquad +\int F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
\eta^{\theta}_{s}(dx)\bigg\} ds
\end{aligned}    
\end{equation}
is a martingale.
Therefore, taking expectations, we have
\begin{equation}\label{eq: Total mass control generalised}
\begin{aligned}
&\mathbb{E}[\langle 1 ,\eta^{\theta}_{t}\rangle] \\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] \\
&+ \int_{0}^{t}\mathbb{E}\bigg\langle
        \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
            \left| \theta \int_{\mathbb{R}^n}
                    \big\{r\big(\rho_{r}*\eta^{\theta}_s(y)\big)-r\big(\rho_{r}*\eta^{\theta}_s(x)\big)\big\}
                    \rho_{1/\theta}(x-y)dy\right| + C_F 
                            ,\eta^{\theta}_s(dx)  \bigg\rangle ds\\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \langle 1  ,\eta^{\theta}_s(dx) \rangle ds,
\end{aligned}
\end{equation}
where the last inequality holds by Lemma \ref{lem: gamma - r radius comparison}.

@@

\subsubsection{Tightness of $(\langle f, \eta^{\theta}_t \rangle )_{t>0}$}
\begin{theorem}[Tightness of $(\langle f, \eta^{\theta}_t \rangle )_{t>0}$]
    \label{teo: Tightness of real-valued projections}
For all $f \in C^{2}_{0}(\mathbb{R}^d)$, 
the process
$(\langle f, \eta^{\theta}_t \rangle)_{t \geq 0}$ is tight.
\end{theorem}
\begin{proof}
We apply the Aldous-Rebolledo criterion \cite{rebolledo:1980}.
It suffices to show that for all stopping time
$\tau \in [0,T]$ and for each $\epsilon>0$, there exists $\delta>0$ and $\theta_0>0$ such that 
\begin{equation}
\begin{aligned}
\sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\mathbb{P}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle
                        - \langle f, \eta^{\theta}_{\tau}\rangle
                \right|> \epsilon \right]
                & < \epsilon;\\
\sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\mathbb{P}\left[\big| [M^{\theta}_{\tau+s}(f)] 
                        - [M^{\theta}_{\tau}(f)] \big|
                        > \epsilon\right]
                & < \epsilon.
\end{aligned}    
\end{equation}
Note that
\begin{equation}
\begin{aligned}
 & \mathbb{E}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle - \langle f, \eta^{\theta}_{\tau}\rangle \right|\right] \\
\leq & \mathbb{E}\Bigg[\bigg| \int_{\tau}^{\tau+s}\bigg\langle \theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x)) \int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{\theta}_{s}(y))-f(x)r(\rho_{r}*\eta^{\theta}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
& \qquad + F(\rho_{F}*\eta^{\theta}_{s}(x)) f(x),\eta^{\theta}_{s}(dx)  \bigg\rangle ds \bigg|\Bigg].
\end{aligned}
\end{equation}
In particular,
\begin{multline}
 \theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{f(y)r(\rho_{r}*\eta^{\theta}_{s}(y))-f(x)r(\rho_{r}*\eta^{\theta}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy \\
 =  f(x)\theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{r(\rho_{r}*\eta^{\theta}_{s}(y))-r(\rho_{r}*\eta^{\theta}_{s}(x))\big\}\rho_{1/\theta}(x-y)dy\\
 + \theta\gamma(\rho_{r}*\eta^{\theta}_{s}(x))\int_{\mathbb{R}^n} \big\{(f(y)-f(x))r(\rho_{r}*\eta^{\theta}_{s}(y))\big\}\rho_{1/\theta}(x-y)dy\\
 \leq C_{\gamma,r}||f||_{\infty} + C_{\gamma}||\Delta f||_{\infty},
\end{multline}
since the first term is bounded above by $C_{\gamma,r}f(x)$ by Lemma \ref{lem: gamma - r radius comparison}
and the second term by $C_{\gamma} \Delta f(x)$ as $r \leq 1$.

Finally,  $F(\rho_{F}*\eta^{\theta}_{s}(x)) f(x)$ is bounded above by $C_F||f||_{\infty}$, so 
\begin{multline}
\mathbb{E}\left[\left|
                        \langle f, \eta^{\theta}_{\tau+s}\rangle - \langle f, \eta^{\theta}_{\tau}\rangle
                \right|\right] \\
\leq (C_{\gamma,r}||f||_{\infty}
        + C_{\gamma,r}||\Delta f||_{\infty}
            +C_F||f||_{\infty})
    \mathbb{E}\bigg\{
                        \int_{\tau}^{\tau+s}
                        \bigg\langle 1,\eta^{\theta}_{s}(dx)  \bigg\rangle 
                        ds
                \bigg\} \\
\leq (C_{\gamma,r}||f||_{\infty}
            + C_{\gamma,r}||\Delta f||_{\infty}
                    +C_F||f||_{\infty})
                \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]
                        e^{(C_{\gamma,r}+C_F)T}(e^\delta-1).
\end{multline}
As $\eta^{\theta}_0$ converges weakly,
we have that 
$\sup_{\theta > \theta_0}\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] < K$
for some $K>0$.
Applying Markov's Inequality,
we can pick small enough $\delta > 0$ such that 
\begin{equation}
\begin{aligned}
\sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\mathbb{P}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle
                        - \langle f, \eta^{\theta}_{\tau}\rangle
                \right|> \epsilon \right]
& \leq \sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\frac{
\mathbb{E}\left[\left| \langle f, \eta^{\theta}_{\tau+s}\rangle
                        - \langle f, \eta^{\theta}_{\tau}\rangle
                \right| \right]
        }{\epsilon}\\
& < \frac{(C_{\gamma,r}||f||_{\infty}
            + C_{\gamma,r}||\Delta f||_{\infty}
                    +C_F||f||_{\infty})
                Ke^{(C_{\gamma,r}+C_F)T}(e^\delta-1)
         }{\epsilon}\\
& < \epsilon.
\end{aligned}    
\end{equation}
Similarly, the control on the second moment is given by Equation \eqref{eq: Control quadratic variation}.
\begin{equation}
    \label{eq: Controlling Quadratic Jumps}
\begin{aligned}
& \sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}\mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] - [M^{\theta}_{\tau}(f)] \big|\right]\\
\leq &\frac{\theta}{N} \mathbb{E} \Bigg\{ \int_{\tau}^{\tau+s}\bigg|
\langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
\int f^2(y)r\big(y,\rho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
,\eta^{\theta}_{s}(dx)\rangle\\
& \qquad \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
,\eta^{\theta}_{s}(dx)\rangle \bigg|ds \Bigg\}\\
\leq & \frac{2\theta}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma(\rho_{\gamma}*\eta^{\theta}_{s}(x))r(\rho_{r}*\eta^{\theta}_{s}(x)), \eta^{\theta}_{s}(dx) \right\rangle ds\Bigg\} \\
& + \frac{1}{N}\mathbb{E} \Bigg\{\int_{\tau}^{\tau+s} \left\langle \gamma (\rho_{\gamma}*\eta^{\theta}_{s}(x))\theta\int_{\mathbb{R}^n}\left(r(\rho_{r}*\eta^{\theta}_{s}(y))-r(\rho_{r}*\eta^{\theta}_{s}(x))\right) q_\theta(x,dy), \eta^{\theta}_{s}(dx) \right\rangle ds\Bigg\}\\
\leq & \frac{(2 \theta C_{\gamma,r}+C_{\gamma,r})\mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle]e^{(C_{\gamma,r}+C_F)T}(e^\delta-1)}{N}.
\end{aligned}
\end{equation}
As $\theta / N \to \alpha$ as $\theta \to \infty$,
there exists some $K'>0$ such that 
$\sup_{\theta > \theta_0} \theta / N < K'$.
An application of Markov's inequality proves that
for small enough $\delta > 0,$
\begin{equation}
\begin{aligned}
\sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\mathbb{P}\left[\big| [M^{\theta}_{\tau+s}(f)] 
                        - [M^{\theta}_{\tau}(f)] \big|
                        > \epsilon\right]
&\leq  \sup_{\theta > \theta_0}
\sup_{s \in [0, \delta]}
\mathbb{E}\left[\big| [M^{\theta}_{\tau+s}(f)] 
                        - [M^{\theta}_{\tau}(f)] \big|
                        \right]/\epsilon \\
&< K'e^{(C_{\gamma,r}+C_F)T}(e^\delta-1)/\epsilon < \epsilon.
\end{aligned}    
\end{equation}
\end{proof}

\subsubsection{Tightness of $(\eta^{\theta}_t)_{t \geq 0}$}
\begin{theorem}
The collection of measure-valued processes 
$\{(\eta^{\theta}_t)_{t \geq 0}: \theta > 0\}$
is tight in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_F(\overline{\mathbb{R}^d}))$.
\end{theorem}
\begin{proof}
To prove relative compactness 
of the processes $(\eta^{\theta}_t)_{t \geq 0}$,
we apply Theorem 3.9.1. in \cite{EK}.

First of all, the set of measures 
$\{ \mu: \langle 1, \mu \rangle \leq K \} $
is compact in $\mathcal{M}_F(\overline{\mathbb{R}^d})$.
Therefore, by Lemma \ref{lem: Compact Containment},
our processes satisfy the compact containment condition.

Secondly, the set of functions $\mathcal{C}^{2}_{0}(\overline{\mathbb{R}^d})$ is a dense subset of all continuous functions on $\mathcal{M}_f(\overline{\mathbb{R}^d})$
under the topology of uniform convergence in compact sets.

Furthermore,
since each measure $\eta^{\theta}_t$ is concentrated in $\mathbb{R}^d$,
it suffices to show that the real-valued processes
$\langle f, \eta^{\theta}_t \rangle$
is tight for all $f \in \mathcal{C}^{2}_{0}(\mathbb{R}^d)$,
which is proven in
Theorem \ref{teo: Tightness of real-valued projections}.
\end{proof}

@@

Before we prove convergence, we define our limit $(\eta^{\infty}(t))_{t>0}$ as a solution to a Martingale Problem with generator $\Pgen$.
